Fluid-mechanical erosion creates anisotropic porous media

### 2022-06-10 docs/PhysicsPaper/StokesErosion.tex
worked on sec 3

It is convenient to write equation~\eqref{eqn:velocityDLP} in terms of
complex variables. With this reformulation, analytic function theory can
be used to show that a particular quadrature rule achieves spectral
accuracy. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
similar notation for $\yy$, and $\nn$. Then, the Stokes double-layer
potential is 
\begin{align}
  \DDD[\eta](x) = \pderiv{}{x} \Re \frac{1}{2\pi i} \int_\Gamma
    \frac{\overline{y \eta(y)}}{x-y} dy + 
\end{align}

>>>>

It is convenient to write equation~\eqref{eqn:velocityDLP} in terms of
complex variables. With this reformulation, simple quadrature rules
achieve spectral accuracy. We identify $\xx = (x_1,x_2)$ with $x = x_1 +
ix_x$, and use similar notation for $\yy$, $\nn$, and $\eeta$. We also
interpret $\Gamma$, the boundary of the domain, as a collection of
Jordan curves in $\CC$. We next introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
Then, we next define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\Gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\Gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\Gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\Gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\Gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
The boundary data of each of these Cauchy integrals satisfies the
Sokhotski-Plemelj jump relation
\begin{align}
  \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\Gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\sigma(x_0) - 
    \frac{1}{2\pi i} \int_{\Gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \Gamma,
\end{align}
where the last integral is interpreted in the principal value sense.

Then, the first and second components of the Stokes double-layer
potential are
\begin{align}
  u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
           \Re(v_3'(x)) + \Re(v_4(x)) \\
  u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
           \Im(v_3'(x)) + \Re(v_5(x)),
\end{align}
respectively.
